%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
   {M.E. in Pattern Recognition and Intelligent System}
   {Graduate University of Chinese Academy of Sciences}
   {Beijing, China}
   {Sep. 2008 - July. 2011}
   {
     \begin{cvsubentries}
       \cvsubentry
         {}
         {Ultrasound Medical Image Segmentation}
         {2009-2011}
         {Working under suppervisation from world prominent wearable devices and body sensor network scientist YT Zhang, my research focused on processing of vascular ultrasound medical images, segmentation and get a key value called IMT, a key factor to evaluate the risk of vascular disease. I learned QT toolkit, and ITK \& VTK image processing and visulization sdk, to fullfill the research task.}
       \cvsubentry
         {}
         {Research Assistant}
         {2010}
         {I got a research assistant position in Chinese University of HongKong, it was a 3 months short term program in the area of wearable medical devices.}
       \cvsubentry
         {}
         {Volunteer}
         {2009-2011}
         {I worked as a volunteer for about five times during internation academic meeting and exhibitions.}
     \end{cvsubentries}
   }
   
  \cventry
    {B.E. in Biomedical Engineering} % Degree
    {Shandong University} % Institution
    {Jinan, China} % Location
    {Sep. 2004 - July. 2008} % Date(s)
    {
      \begin{cvsubentries} % Description(s) bullet points
        \cvsubentry
          {}
          {3rd Scholarship For Academic Performance}
          {2005}
          {}
        \cvsubentry
          {}
          {2nd Scholarship For Academic Performance}
          {2006}
          {}
        \cvsubentry
          {}
          {Interchange Plan}
          {2006-2007}
          {Selected to join one-year interchange plan with Tianjin University}
        \cvsubentry
          {}
          {Remote Monitor System}
          {2006-2007}
          {I worked on a Samsung ARM7 based develop board, connected with a u-blox GPS module and a Semense GSM module. The system got the location of the disable and send SMS to the family members. During the developing process, I ported a ucOS to the ARM7 processor, which offered me great chance to understand how S.W and H.W work together. And this is the first step to what I am doing today.}
        \cvsubentry
          {}
          {3rd Scholarship For Academic Performance}
          {2007}
          {}
        \cvsubentry
          {}
          {1st Award In National Electronics Design Competetion}
          {2007}
          {With our excelent performance in the designing of a signal splitter to measure the composition frequencies and powers of given signal, we won the 1st Award.}
        \cvsubentry
          {}
          {Graduate Examination Exemption}
          {2007}
          {Recommened to further study in Graduate University of Chinese Academy of Sciences with entrance examination exemption, for my academic performance and design practice in electronic design.}
      \end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
